\subsection{Data}

We will be using the data compiled by James Fowler on the $93^{rd}$ through
$110^{th}$ congress. This data includes the ICPSR id number for each
representative, the bills that they have sponsored or cosponsored, and the date
of these events.  Further, we have data on when a bill was created and when and
if it was passed into law.

We have additional supplementary data on candidates and bills. Much of it is
compiled by govTrack, which is an entity that scrapes and compiles congressional
data from congress.gov. govTrack has more granular detail about each bill beyond
its existence and ultimate outcome, including the  entirety of the text, what
happened to a bill during each stage of the  bill's life (such as passage
through committee), and who voted for and against a bill. It also has more
information about each Congressperson, including their partisanship, state or
district, and committee memberships. We also draw upon ideology information (DW-
Nominate scores) about each legislator.

In total, this comprises approximately $1000$ representatives (nodes) and about
$350000$ bills (potential edges). This amounts to about $500$ Mbs of graph
data. In additon, the storage size of the metadata of all bills is
approximately $1$ Gb. Depending on the method we use to generate a network,
there is the possibility of it being quite dense; for example, if we create an
edge when two Congresspeople cosponsor at least 10 bills together, almost a
fifth of all possible edges are created.
