\subsection{CESNA Clustering Description}

We are interested in analyzing clusters of legislators based on their network of
working relationships. Crucially, we are particularly important in how these
clusters relate to the attributes of the legislators. A promising approach is
laid out in Yang et al.~\cite{Yang}, who describe an algorithm for finding
Communities from Edge Structure and Node Attributes, which they call CESNA.
CESNA incorporates node features and edge structure to find communities instead
of just relying on one or the other. It explicitly computes the importance of
different node features in forming each cluster. Additionally, it allows for
overlapping and nested communities, which is one of the key features of our
dataset. Legislators are likely to have distinct communities of working
relationships with their regional peers, ideological peers, committee peers, and
of course party peers.

In particular, we make use of the authors' C++ implementation and feed in
details of our own network. As is necessary for the models, we binarize all of
our variables. This means that categorical variables like region are split into
distinct dummy variables and continuous variables like ideology are split into
buckets. We choose to split each ideological dimension into five groups: left,
center-left, moderate, center-right, and right, each of which roughly contain a
fifth of the members. The motivation behind selecting an odd number of groups is
to allow for a moderate group that straddles the DW-NOMINATE center point of 0.
The final list of variables, appropriately binarized, are party, ideology,
region, committee, gender, and age.
